---
title: "1-tcd_pre-processing_tiling"
author: "Benjamin Labohm"
date: "`r Sys.Date()`"
output: html_document
---

# Harmonized forest area and condition processing on 1km resolution
# 1. Aggregate forest condition inside stable forest
# 2. Calculate forest area
# 3. Calculate sensitivity layers
# 4. Assemble and mask data sets
# NOTE: This script will execute a process in parallel on 60% of the available computational cores. This might render the machine useless for other tasks at the same time.

## Setup
```{r setup, include=FALSE}

# Use github directory as working directory (might change data directory)
working_directory <- "D:/github/forest_dynamics/"
data_directory <- paste0(working_directory, "data/")

# Load custom functions for this project
source(paste0(working_directory,
              "processing/2_tcd_processing_Step_1_and_2_general_funs.R"))
source(paste0(working_directory, 
              "processing/2_tcd_processing_Step_1_funs.R"))

# List input files for 2012 and 2018 and gather them in a list
data_df <- mkDatDf(data_directory)
data_list <- split(data_df, data_df$n)

```

## 1. Forest condition
```{r Forest condition, eval=FALSE}

# Execute forest condition change calculation
to_do <- find_missing(paste0(data_directory, "TCD12_stable_forest/"),
                      nrow(data_df))
if (!is.null(to_do)) data_list <- data_df[to_do,] %>% split(., .$n)

par_exec(data_list, 
         fun = tcd_change_stable_forest, 
         perc_cores = .6)

```

## 2. Forest area
```{r Forest area, eval=FALSE}

# Execute forest area change calculation
to_do <- find_missing(paste0(data_directory, "TCA12/"), 
                      nrow(data_df))
if (!is.null(to_do)) data_list <- data_df[to_do,] %>% split(., .$n)

par_exec(data_list, 
         fun = tca_change, 
         perc_cores = .6)

```

## 3. Sensitivity layers
```{r Sensitivity layers, eval=FALSE}

#Execute sensitivity layer calculation
to_do <- find_missing(paste0(data_directory, "na12/"), 
                      nrow(data_df))
if (!is.null(to_do)) data_list <- data_df[to_do,] %>% split(., .$n)

par_exec(data_list, 
         fun = sensitivity_lyrs, 
         perc_cores = .6)

```


4. Assemble and mask
```{r Assemble and mask data sets, eval=FALSE}

# List output of parallel processing
tile_dirs <- list.dirs(data_directory, recursive = FALSE) %>%
  .[grepl("tile", .)]

no_data_mask <- rast(paste0(data_directory, ""))

# Put individual tiles in a vrt and write them to file
for (t_dir in tile_dirs) {
  
  out_vrt <- list.files(t_dir, full.names = TRUE,
                        pattern = ".tif$") %>%
    vrt() 
  
  out_vrt_masked <- mask(out_rst, 
                         no_data_mask,
                         maskvalue = 1,
                         updatevalue = 255)
  
  writeRaster(out_vrt_masked, paste0(t_dir, ".tif"))
}

```

